---
title: "MidtermReport"
author: "Lee Che Yuet Isaac"
date: "3/31/2023"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
# Progress so far

Preparation for the datasets are almost done, then can be moved on to the matching phase. There is a minor problem regarding including states as a covariate for matching, which is still considering for a solution.




# Initialization

```{r, results = 'hide', message = FALSE}
rm(list=ls())
gc()
```

```{r message=FALSE, warning=FALSE, include=FALSE}
# required packages
packages <- c('readr','dplyr', 'AER','stargazer','haven','cem','Matching','MatchIt','cobalt')

# install any packages that are not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# load required packages
invisible(lapply(packages, library, character.only = TRUE))
```

# Vaccine incentives
## Loading the dataset as tibble
```{r Loading the dataset as tibble,message=FALSE, warning=FALSE, paged.print=TRUE}
# load dataset
vaccine_incentives <- read_delim("analysis_ready.csv",
delim = ";", escape_double = FALSE, trim_ws = TRUE) %>% # need to change the folder path
  as_tibble()

#glimpse
head(vaccine_incentives)
```


```{r Counting experimental groups by treatment}
count(vaccine_incentives, Treatment)
```
```{r Counting experimental groups by names}
count(vaccine_incentives, Treatment2)
```
Control: treatment1(CDC Health Information)  
Treatment version 1: treatment2(Lottery Incentive)  
Treatment version 2: treatment3(Cash Voucher Incentive)  

## Data cleaning
```{r Data cleaning, message=FALSE, warning=FALSE, paged.print=TRUE}
vi_cleaned <- vaccine_incentives %>%
  mutate(
    Treatment_012 = case_when(Treatment == 'treatment1' ~ 0,
                             Treatment == 'treatment2' ~ 1,
                             Treatment == 'treatment3' ~ 2),
    Female_10 = case_when(gender == 'Female' ~ 1,
                     gender == 'Male' ~ 0,
                     gender == 'Other' ~ NA_real_),
    age_young_10 = if_else(Age_cat == 'Young', 1, 0),
    race_white_10 = if_else(Race == 'White' , 1, 0),
    race_black_10 = if_else(Race == 'Black' , 1, 0),
    race_other_10 = if_else(Race == 'Other' , 1, 0),
    education_low_10 = if_else(Education == 'Low' , 1, 0),
    education_medium_10 = if_else(Education == 'Medium' , 1, 0),
    education_high_10 = if_else(Education == 'High' , 1,0),
    pool_CloudResearch_10 = if_else(pool == 'CloudResearch' , 1, 0),
    pool_Facebook_10 = if_else(pool == 'Facebook' , 1, 0),
    pool_Lucid_10 = if_else(pool == 'Lucid' , 1, 0),
    outcome = if_else(clicked == 1, 1, 0),
    treated = if_else(Treatment_012 > 0, 1, 0)) %>%
  dplyr::select(Treatment_012,
                Female_10,
                age_young_10,
                race_white_10,
                race_black_10,
                race_other_10,
                education_low_10,
                education_medium_10,
                education_high_10,
                pool_CloudResearch_10,
                pool_Facebook_10,
                pool_Lucid_10,
                Trumppercent,
                Trumphi,
                age,
                outcome,
                treated)

head(vi_cleaned)
```
## Summary statistics
```{r Summary statistics}
vi_cleaned %>%
  mutate(
    Treatment_012 = factor(Treatment_012),
                Female_10 = factor(Female_10),
                age_young_10 = factor(age_young_10),
                race_white_10 = factor(race_white_10),
                race_black_10 = factor(race_black_10),
                race_other_10 = factor(race_other_10),
                education_low_10 = factor(education_low_10),
                education_medium_10 = factor(education_medium_10),
                education_high_10 = factor(education_high_10),
                pool_CloudResearch_10 = factor(pool_CloudResearch_10),
                pool_Facebook_10 = factor(pool_Facebook_10),
                pool_Lucid_10 = factor(pool_Lucid_10),
                Trumppercent,
                Trumphi = factor(Trumphi),
                age,
                outcome = factor(outcome),
    treated = factor(treated)
  ) %>%
  summary() 
```
## Experimental benchmark
Creating a basic and preliminary estimate of the treatment effect.
```{r Experimental benchmark basic regression}
model_vi_1 <- lm(outcome ~ treated, data = vi_cleaned)
summary(model_vi_1)
```
Try adding other covariates into the regression and se
```{r Experimental benchmark regression with control}
model_vi_2 <- lm(outcome ~ treated + 
                   Female_10 +
                   age_young_10 +
                   race_white_10 +
                   race_black_10 +
                   race_other_10 +
                   education_low_10 +
                   education_medium_10 +
                   education_high_10 +
                   pool_CloudResearch_10 +
                   pool_Facebook_10 +
                   pool_Lucid_10 +
                   Trumppercent +
                   Trumphi +
                   age, data = vi_cleaned)
summary(model_vi_2)
```


## Matching preparation
```{r Matching preparation}
tr <- which(vi_cleaned$treated == 1)
ct <- which(vi_cleaned$treated == 0)
ntr <- length(tr)
ntr
nct <- length(ct)
nct
```
## Basic estimate
```{r Basic estimate}
mean(na.omit(vi_cleaned$outcome[tr])) - mean(na.omit(vi_cleaned$outcome[ct]))
```
## Covariate balance
```{r Covariate balance, message=FALSE, warning=FALSE}
covs1 <- vi_cleaned %>%
  dplyr::select(Treatment_012,
                Female_10,
                age_young_10,
                race_white_10,
                race_black_10,
                race_other_10,
                education_low_10,
                education_medium_10,
                education_high_10,
                pool_CloudResearch_10,
                pool_Facebook_10,
                pool_Lucid_10,
                Trumppercent,
                Trumphi,
                age,
                treated) %>%
  na.omit()

bal.tab(covs1, treat = covs1$treated)
```



# Email mobilization
```{r include=FALSE}
# load dataset: email_mobilization
email_mobilization <- read_csv("subset_finalAnalysisFile20170711.csv") %>% # need to change the folder path
  as_tibble()
```

Have a glimpse on the dataset.

```{r}
head(email_mobilization)
```

Look into the distribution of the experimental groups.

    1.  `0`: Control
    2.  `1`: Election Information
    3.  `2`: Social Pressure
    4.  `3`: Native Threat
    5.  `4`: Latino Group Threat.
```{r}
count(email_mobilization, treat)
```

## Summary statistics of the whole dataset
Some of the variables are binary indicators so they are converted into factors.
```{r}
email_mobilization %>%
  # turn binary indicators into factors so that we can get more useful summaries
  mutate(gender = factor(gender), 
         race = factor(race),
         party = factor(party), 
         voterStatus = factor(voterStatus),
         congressionalDistrict = factor(congressionalDistrict),
         general16 = factor(general16),
         outcome = factor(outcome),
         historyCode2016 = factor(historyCode2016), 
         recent = factor(recent),
         likely = factor(likely),
         general12 = factor(general12),
         treat = factor(treat),
         registered_prior = factor(registered_prior),
         minority = factor(minority),
         major_party = factor(major_party),
         validEmail = factor(validEmail),
         pastGeneral = factor(pastGeneral)
         ) %>%
  summary()
```
## Create the experiment subset
Filtering out the observations that are not in the experimental groups.
```{r} 
em_experiment <- email_mobilization %>%
  filter(treat != 'NA') %>%
  as_tibble()

  
head(em_experiment)
```
Double checking the distribution of the experimental groups.
```{r}
count(em_experiment, treat)
```
## Summary statistics of the whole dataset
Some of the variables are binary indicators so they are converted into factors.   
```{r}
em_experiment %>%
  # turn binary indicators into factors so that we can get more useful summaries
  mutate(gender = factor(gender), 
         race = factor(race),
         party = factor(party), 
         voterStatus = factor(voterStatus),
         congressionalDistrict = factor(congressionalDistrict),
         general16 = factor(general16),
         outcome = factor(outcome),
         historyCode2016 = factor(historyCode2016), 
         recent = factor(recent),
         likely = factor(likely),
         general12 = factor(general12),
         treat = factor(treat),
         registered_prior = factor(registered_prior),
         minority = factor(minority),
         major_party = factor(major_party),
         validEmail = factor(validEmail),
         pastGeneral = factor(pastGeneral)
         ) %>%
  summary()
```
## Experimental benchmark
Creating a basic and preliminary estimate of the treatment effect.
```{r}
em_experiment <- em_experiment %>%
  mutate(treated = case_when(treat == 0 ~ 0,
                             treat > 0 ~ 1),
         democrat = case_when(major_party == 1 ~ 1,
                              major_party > 1 ~ 0),
         female = if_else(gender == "F", 1,0),
         non_white = if_else(minority == 1,1,0))
         

model_em_1 <- lm(outcome ~ treated, data = em_experiment)
summary(model_em_1)
```
Try adding other covariates into the regression and se
```{r}
model_em_2 <- lm(outcome ~ treated + 
                   gender +
                   age +
                   race +
                   major_party +
                   minority
                   , data = em_experiment)
summary(model_em_2)
```
## Coarsened Exact Matching
```{r}
tr <- which(em_experiment$treated == 1)
ct <- which(em_experiment$treated == 0)
ntr <- length(tr)
ntr
nct <- length(ct)
nct
```
### Basic estimate
```{r}
mean(na.omit(em_experiment$outcome[tr])) - mean(na.omit(em_experiment$outcome[ct]))
```
### Covariate balance
```{r}
vars <- c("democrat", "age", "female", "non_white","treated")
covs1 <- na.omit(em_experiment[,vars])
bal.tab(covs1, treat = covs1$treated)
```
### Coarsening 1
```{r eval=FALSE, include=FALSE}
cem1_var <- c("democrat", "age", "female", "non_white","treated", "outcome")
data1 <- na.omit(em_experiment[,cem1_var])

X_1 <- data1 %>%
  dplyr::select(democrat, age, female, non_white, treated, outcome)

m.out.cem <- matchit(treated ~ democrat + age + female + non_white,
                     data = data1, method = "cem")

bal_tab_cem <- bal.tab(m.out.cem, thresholds = c(m = 0.1), un = TRUE)
bal_tab_cem
```
```{r eval=FALSE, include=FALSE}
lp.cem <- love.plot(
  m.out.cem,
  threshold = .1,
  binary = 'std',
  treat = data1$treated,
  covs = X_1)

lp.cem
```
### ATT by CEM
```{r eval=FALSE, include=FALSE}
m.data.cem <- match.data(m.out.cem)
m.data.cem
```
### cem regression 
```{r eval=FALSE, include=FALSE}
lm.cem1 <- lm(outcome ~ treated, data = m.data.cem)
summary(lm.cem1)
```
```{r eval=FALSE, include=FALSE}
lm.cem2 <- lm(outcome ~ treated +
                democrat +
                age +
                female +
                non_white, data = m.data.cem)
summary(lm.cem2)
```
# Genetic matching
```{r eval=FALSE, include=FALSE}
set.seed(1)
m.out.gen <- matchit(treated ~ democrat + age + female + non_white, data = data1, replace = TRUE, method = "genetic")
bal_tab_gen <- bal.tab(m.out.gen, thresholds = c(m = 0.1), un = TRUE)
bal_tab_gen
```
```{r eval=FALSE, include=FALSE}
lp.gen <- love.plot(
  m.out.gen,
  threshold = .1,
  binary = 'std',
  treat = data11$past_pkpres,
  covs = X_11
)

lp.gen
```
## Nearest neighbour matching
```{r eval=FALSE, include=FALSE}
m.out.nnm <- matchit(treated ~ democrat + age + female + non_white, data = data1, replace = TRUE, method = "nearest")
bal_tab_nnm <- bal.tab(m.out.nnm, thresholds = c(m = 0.1), un = TRUE)
bal_tab_nnm
```
```{r eval=FALSE, include=FALSE}
lp.nnm <- love.plot(
  m.out.nnm,
  threshold = .1,
  binary = 'std',
  treat = data11$treated,
  covs = X_11
)

lp.nnm
```





# To-do:

matching

covariate balance

summary statistics

comparison between the datasets
